\emph{Specific Aim 3:} To map each of the 11 NSQIP variables used by mFI to ICD10 codes and lab values in the electronic medical record system.


\subsection{Research Strategy}\label{research-strategy}


\subsubsection{Significance}\label{significance}

\subsubsection{Innovation}\label{innovation}

\paragraph{Preliminary Studies and Feasibility}\label{preliminary-studies-and-feasibility} This is a test.


\paragraph{Study Design}\label{study-design}


\paragraph{Study Population}\label{study-population}


\paragraph{Study Procedures}\label{study-procedures}


\paragraph{Data Analysis}\label{data-analysis}

\paragraph{Power and Sample Size}\label{power-and-sample-size}

\paragraph{Expected Outcomes}\label{expected-outcomes}

\paragraph{Potential Problems and Alternative
      Approaches}\label{potential-problems-and-alternative-approaches}

\paragraph{Future Directions}\label{future-directions} 
    
\section{Ammo (Temporary Storage, Not Part of Final Document)}\label{ammo}
There are two main types of frailty scores used in geriatric research and clinical practice: the Fried frailty phenotype \cite{Fried_2001} and the Rockwood Frailty Index \cite{Mitnitski_2001}. The frailty phenotype is anchored on weakness, sarcopenia, diminished mobility as recorded via patient questionnaire or an physical assessment performed by a physician. The frailty index is based on the deficit accumulation theory and is calculated as a simple unweighted sum of selected diagnoses, conditions, and dichotomized lab values, corrected for missing observations. The actual choice of variables is less important than them spanning multiple clinical domains \cite{Searle_2008}. 

\subsection{Link to Aging}\label{link-to-aging}

\subsection{Clinical Impact}\label{clinical-impact}
Registries such as ACS NSQIP offer the advantage of high quality expert-curated data with clearly defined guidelines and good inter-rater reliability \cite{Shiloach_2010}. Registry data is of limited use in clinical decision support: it includes only a subset of patients from each participating site, it includes only a pre-determined set of variables, and most importantly, it can only be used retrospectively after a registrar has performed the necessary chart abstraction. In other words, predictors bound to registries cannot be used to create real-time alerts recommending, for example, less invasive treatment options or a geriatric consult prior to surgery. Nevertheless, ACS NSQIP can be a good proving ground for algorithms that can then be migrated to the electronic medical record (EMR). First, a copy of a health-system's local NSQIP registry is obtained \textit{with} patient identifiers still included (as I have done in support of Dr. Shireman's Pepper Center Pilot project on frailty as a predictor of post-operative complications in older patients). Then, a frailty measure previous validated on NSQIP data is re-created; in this case the frailty measure was the Administrative Risk Analysis Index (RAI-A) \cite{Hall_2017,Johnson_2014,Melin_2015,Gupta_2011}. Next, under the supervision of an experienced clinician and reference to the NSQIP Participant Use Data File (PUF), the equivalent diagnosis codes (ICD10) and laboratory values need to be matched in the EMR system and adjusted until their predictions converge the registry-based ones, for the same respective patients.

Though Dr. Shireman's and Dr. Espinoza's Pilot Project and the R21 that resulted from it rely on the RAI-A, for my own project I intend to apply what I learned to the Rockwood Index because it is more robust than RAI-A, is in use by both geriatricians and surgeons [todo: find refs for how geriatricians actually use it to collaborate with surgeons], and has a statistically sound grounding in bio-gerontology -- briefly, a patient's Rockwood Index can be used to construct a hazard model  \cite{Mitnitski_2001} similar to the Gompertz function \cite{Mueller_1995,Pletcher_2000,Bokov_2017}.

A widely used variant of the Rockwood Index used by surgeons and validated against NSQIP is called the modified Frailty Index (mFI) \cite{Uppal_2015,Tsiouris_2013,Bellamy_2017,22491599,23711971,23949353}. Not all sites participating in NSQIP support all the variables used by mFI, including ours. However, Rockwood has also published a \textit{methodology} for developing a frailty index that has a high degree of agreement with other indexes developed using the same methodology. This, for the purposes of this research project, is what I mean by the Rockwood Index (for preliminary version of this index have already started testing, see Research Plan section below).

\emph{Specific Aim 1:} To finish development and internal validation of the preliminary Rockwood Index I developed using NSQIP data. This will involved the following steps:
\begin{itemize}
\item Under the guidance of my geriatric and surgical mentors, internal EMR value-flags, and the relevant literature, I will identify age-adjusted reference ranges for the NSQIP laboratory values and use them to dichotomize those values into normal/abnormal, so that they can also be included in the Rockwood Index.
\item I will determine whether there is convergent validity with RAI-A and predictive validity for postoperative complications and readmissions.
\item I will determine whether the predictions and parameter distributions are stable under resampling. I will then further validate the predictions of my model against the hold-out validation subset of the data.
\end{itemize}

\emph{Specific Aim 2:} To link our NSQIP dataset to long-term outcomes that are relevant to healthy aging and determine whether the Rockwood index needs to be adjusted for socioeconomic covariates. In particular:
\begin{itemize}
\item To build on the my previous EMR geocoding work by matching patient address histories to the addresses of nursing homes and hospices, so that the transition from private addresses could serve as  proxy variable for loss of independence.
\item To validate and refine the address-matching rules using as a standard the 554 NSQIP patients with complete records and discharge destinations other than their homes.
\item To determine which, if any, adjustments for patient ethnicity or income will further improve predictive accuracy.
\end{itemize}

\emph{Specific Aim 3:} To migrate the Rockwood Index to the EMR system and demonstrate that it remains consistent with the NSQIP version. This will entail the following steps:
\begin{itemize}
\item To work with my geriatric and surgical mentor/s to identify groups EMR data elements that have the reliably correspond to NSQIP variables.
\item To determine whether there strong agreement between the NSQIP and EMR versions of the Rockwood Index, and whether the EMR version has improved prediction of long-term survival and independence compared to the NSQIP version.
\item To determine whether the Rockwood Index is effective in predicting other well-established sequelae of frailty (falls and lower limb fractures, pneumonia, outpatient readmissions, and death) in a the larger population of the EMR and no longer limited to surgery cases.
\end{itemize}


